r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2020-11-13 r-package/paper2020/paper2020.Rmd
update paper plot

ggplot(data=plot_data, aes(y = travel_time, x = reorder(fromId, mediantt))) +
  geom_point(alpha = 0.05, size = .7) +
  geom_line(aes(y=mediantt, group=toId), color='blue') +
  expand_limits(y = 120) +
  scale_y_continuous(breaks = c(0, 30, 60, 90, 120)) +
  theme_minimal() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(fill = NA, colour = "grey80", size=1)) +
  labs(title = "Travel time variation among percentiles, per OD pair",
       y = "Travel Time (min)")

>>>>

ggplot(data=plot_data, aes(y = travel_time, x = reorder(fromId, mediantt))) +
  geom_point(alpha = 0.05, size = .7) +
  geom_line(aes(y=mediantt, group=toId), color='blue') +
  expand_limits(y = 120) +
  scale_y_continuous(breaks = c(0, 30, 60, 90, 120)) +
  theme_minimal() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.x = element_blank(), 
        axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.border = element_rect(fill = NA, colour = "grey80", size=1)) +
  labs(title = "Travel time uncertainty per destination",
       y = "Travel Time (min)", x='Destinations')
